\textsc{PAPERCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-03-07 paper/hubble_paperclip.tex
Rename files to hubble_paperclip; version sent out for comments

\def\preprintno{XXXX \SM{Requested from Charles}} % Insert correct preprint number

@@

% Define a new fancy page style
\fancypagestyle{firstpage}{
    \rhead{MIT-CTP/\preprintno}
    % Define other header and footer elements if necessary
}

@@

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation \SM{I like `Representation' rather than `Refinement', I think the former emphasizes the central abstracts-as-captions aspect a bit more} for Contrastive Language-Image Pre-training\footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), a method that connects astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals and images corresponding to downstream observations. 
%
Concretely, here we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm.
%

@@

\begin{landscape}
  \begin{table}[h!]
    \renewcommand{\arraystretch}{2}
      \centering
      \begin{tabular}{m{1.8cm} m{8cm} m{5cm} m{6.5cm}}
          \toprule
          \bfseries Prop. ID & \centering\arraybackslash \bfseries Proposal abstract & \multicolumn{2}{c}{\bfseries LLM-extracted summary} \tabularnewline
          \cmidrule(r){3-4}
          & & \centering\arraybackslash \bfseries Objects and phenomena & \centering\arraybackslash \bfseries Science use cases \tabularnewline
          \midrule
          \input{\thedatafolder/id1_2.txt} & {\scriptsize \input{\thedatafolder/abs1_2.txt}} & {\scriptsize \input{\thedatafolder/obj1_2.txt}} & {\scriptsize \input{\thedatafolder/sci1_2.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_1.txt} & {\scriptsize \input{\thedatafolder/abs1_1.txt}} & {\scriptsize \input{\thedatafolder/obj1_1.txt}} & {\scriptsize \input{\thedatafolder/sci1_1.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_3.txt} & {\scriptsize \input{\thedatafolder/abs1_3.txt}} & {\scriptsize \input{\thedatafolder/obj1_3.txt}} & {\scriptsize \input{\thedatafolder/sci1_3.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_0.txt} & {\scriptsize \input{\thedatafolder/abs1_0.txt}} & {\scriptsize \input{\thedatafolder/obj1_0.txt}} & {\scriptsize \input{\thedatafolder/sci1_0.txt}} \tabularnewline
          \bottomrule
      \end{tabular}
      \caption{Examples of the clipped \hubble proposal abstracts (second column) and LLM (\textsc{Mixtral-8x7B})-extracted summaries (right-most two columns), separately extracting objects and phenomena as well as potential downstream science use cases. \SM{Don't rotate?}}
      \label{tab:datasetsumm}
  \end{table}
  \end{landscape}

@@

This work relies on using abstracts from successful \hubble Space Telescope observing proposals as part of a dataset for training and evaluating machine learning models. While these abstracts are publicly accessible, the authors likely did not anticipate their text being used in this manner, raising questions around consent and appropriate use of data. Since this research intends to develop methods to aid astronomical research and does not use sensitive personal information or target commercial gain, we believe that the scientific benefits outweigh the potential concerns in this case while acknowledging good-faith arguments to the contrary. As the use of foundation models in the sciences increases, it will be important for the astronomy community to consider norms and guidelines around the appropriate use and attribution of various data sources for model training and evaluation, including qualitative textual data, to ensure transparency and maintain trust in the community.

@@

\bibliography{main}
\bibliographystyle{tmlr}

@@

The following schema is used to guide the generation of the summaries, intended to produce between one and five objects and hypotheses, as well as science use cases.

@@

The following prompt function is used to produce a list of possible objects and phenomena shown in HST observations downstream of a proposal abstract, as well as one to five possible science use cases.

@@

The following curated categories are used in the text retrieval experiment in Sec.~\ref{sec:results}.
%
These are derived by initially prompting \textsc{Claude 2}, having attached a subsample of 30 proposal abstracts in the online interface to be used as context, to produce a list of categories corresponding to typical HST observations. The list is then manually curated to remove similar entries and ensure a representative sample of categories. \SM{I realized when looking up the prompt that I did actually attach a sample of abstracts as context}

>>>>

\def\preprintno{XXXX} % Insert correct preprint number

@@

% Define a new fancy page style
\fancypagestyle{firstpage}{
    % \rhead{MIT-CTP/\preprintno}
}

@@

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation for Contrastive Language-Image Pre-training\footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), a method that connects astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals and images corresponding to downstream observations. 
%
Concretely, here we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm.
%

@@

\begin{landscape}
  \begin{table}[h!]
    \renewcommand{\arraystretch}{2}
      \centering
      \begin{tabular}{m{1.8cm} m{8cm} m{5cm} m{6.5cm}}
          \toprule
          \bfseries Prop. ID & \centering\arraybackslash \bfseries Proposal abstract & \multicolumn{2}{c}{\bfseries LLM-extracted summary} \tabularnewline
          \cmidrule(r){3-4}
          & & \centering\arraybackslash \bfseries Objects and phenomena & \centering\arraybackslash \bfseries Science use cases \tabularnewline
          \midrule
          \input{\thedatafolder/id1_2.txt} & {\scriptsize \input{\thedatafolder/abs1_2.txt}} & {\scriptsize \input{\thedatafolder/obj1_2.txt}} & {\scriptsize \input{\thedatafolder/sci1_2.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_1.txt} & {\scriptsize \input{\thedatafolder/abs1_1.txt}} & {\scriptsize \input{\thedatafolder/obj1_1.txt}} & {\scriptsize \input{\thedatafolder/sci1_1.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_3.txt} & {\scriptsize \input{\thedatafolder/abs1_3.txt}} & {\scriptsize \input{\thedatafolder/obj1_3.txt}} & {\scriptsize \input{\thedatafolder/sci1_3.txt}} \tabularnewline
          \midrule
          \input{\thedatafolder/id1_0.txt} & {\scriptsize \input{\thedatafolder/abs1_0.txt}} & {\scriptsize \input{\thedatafolder/obj1_0.txt}} & {\scriptsize \input{\thedatafolder/sci1_0.txt}} \tabularnewline
          \bottomrule
      \end{tabular}
      \caption{Examples of the clipped \hubble proposal abstracts (second column) and LLM (\textsc{Mixtral-8x7B})-extracted summaries (right-most two columns), separately extracting objects and phenomena as well as potential downstream science use cases.}
      \label{tab:datasetsumm}
  \end{table}
  \end{landscape}

@@

This work relies on using abstracts from successful \hubble Space Telescope observing proposals as part of a dataset for training and evaluating machine learning models. While these abstracts are publicly available, the authors likely did not anticipate their text being used in this manner, raising questions around consent, attribution, and appropriate use of data. Since this research intends to develop methods to aid astronomical research and does not use sensitive personal information or target commercial gain, we believe that the scientific benefits outweigh the potential concerns in this case while acknowledging good-faith arguments to the contrary. As the use of foundation models in the sciences increases, it will be important for the community to consider norms and guidelines around the appropriate use and attribution of various data sources for model training and evaluation, including qualitative textual data, to ensure transparency and maintain trust.

@@

\bibliography{hubble_paperclip}
\bibliographystyle{tmlr}

@@

The following schema is used to guide the generation of the summaries, intended to produce between one and five objects and hypotheses, as well as science use cases. \\

@@

The following prompt function is used to produce a list of possible objects and phenomena shown in HST observations downstream of a proposal abstract, as well as one to five possible science use cases. \\

@@

The following curated categories are used in the text retrieval experiment in Sec.~\ref{sec:results}.
%
These are derived by initially prompting \textsc{Claude 2}, having attached a subsample of 30 proposal abstracts in the online interface to be used as context, to produce a list of categories corresponding to typical HST observations. The list is then manually curated to remove similar entries and ensure a representative sample of categories. \\
